A Hitchhiker's Guide to Reproducible Research

### 2021-06-09 manuscript.Rmd
install repro from r-universe closes #113

```{r, eval=FALSE}
install.packages("gert")
# repro is not on CRAN yet, install from GitHub
if(!requireNamespace("remotes"))install.packages("remotes")
remotes::install_github("aaronpeikert/repro")
```

>>>>

```{r, eval=FALSE}
install.packages("gert")
# repro is not on CRAN yet
install.packages('repro', repos = 'https://aaronpeikert.r-universe.dev')
```
